---
title: "Analysis of Burge Lab Porter Tasting"
author: "Peter Sudmant"
date: '2018-02-27'
output:
  html_document: default
  pdf_document: default
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

```{r package_options, include=FALSE}
  knitr::opts_chunk$set(fig.width=6, fig.height=3.5,
               echo=FALSE, warning=FALSE, message=FALSE)
```


<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

The code below loads and analyzes the Burge Lab 2018 Porter Tasting Night Results

```{r}
library(dplyr)
library(tidyr)
library(broom)
library(ggplot2)
library(ggrepel)
library(RColorBrewer)
library(cowplot)
library(corrplot)


t= read.table("../data/BurgeLabBeer.tsv", header=T, sep="\t")
t_inf=read.table("../data/info.tsv", header=T, sep="\t") %>%
        mutate(TRUE_ABV = ABV)


t_format=t %>% gather(key="key", 
					  value="value", 
					  -Timestamp, 
					  -Email.Address, 
					  -Name, 
					  -Lab, 
					  -Position, 
					  -Age, 
					  -Sex, 
					  -home) %>%
				separate(key, c("attribute", "beer")) %>%
				mutate(beer=as.numeric(beer))
			
t_format = inner_join(t_format, t_inf, by="beer")
t_format = t_format %>% 
            mutate(beer_name = paste(Brewery, "\n", beer_name, " (", beer, ")", sep=""))

dim(t_format)
```

# OverallPreferences Among Beers
## Taste
```{r}
colors=c("black",brewer.pal(2,"Set1"))

g1=ggplot(t_format %>% filter(attribute %in% c("taste")))
g1=g1+stat_summary(aes(x=reorder(beer_name, value), 
                   y = value, 
                   color=(beer %in% c(1,5))), 
               fun.data = mean_se)+
	theme_classic(base_size=18)+
	scale_x_discrete("")+
	scale_y_continuous("Taste")+
	coord_flip(ylim=c(1,5))+
  theme(legend.position="none")+
  scale_color_manual(values=colors)+
  theme(axis.text.y=element_text(size=8))

g2=ggplot(t_format %>% filter(attribute %in% c("taste")))
g2=g2+geom_histogram(aes(x=value),
                 bins=5,
                 color='black')+
	theme_classic(base_size=18)+
  scale_y_continuous("")+
  scale_x_continuous("")
cowplot::plot_grid(g1,g2,rel_widths=c(.8,.5), rel_heights=c(1,.5),nrow=1,ncol=2)
```

## Aroma
```{r}

g1=ggplot(t_format %>% filter(attribute %in% c("Aroma")))
g1=g1+stat_summary(aes(x=reorder(beer_name, value), 
                   y = value, 
                   color=(beer %in% c(1,5))), 
               fun.data = mean_se)+
	theme_classic(base_size=18)+
	scale_x_discrete("")+
	scale_y_continuous("Aroma")+
	coord_flip(ylim=c(1,5))+
  theme(legend.position="none")+
  scale_color_manual(values=colors)+
  theme(axis.text.y=element_text(size=8))

g2=ggplot(t_format %>% filter(attribute %in% c("Aroma")))
g2=g2+geom_histogram(aes(x=value),
                 bins=5,
                 color='black')+
	theme_classic(base_size=18)+
  scale_y_continuous("")+
  scale_x_continuous("")
cowplot::plot_grid(g1,g2,rel_widths=c(.8,.5), rel_heights=c(1,.5),nrow=1,ncol=2)
```

## Mouth Feel
```{r}

g1=ggplot(t_format %>% filter(attribute %in% c("MF")))
g1=g1+stat_summary(aes(x=reorder(beer_name, value), 
                   y = value, 
                   color=(beer %in% c(1,5))), 
               fun.data = mean_se)+
	theme_classic(base_size=18)+
	scale_x_discrete("")+
	scale_y_continuous("Mouth Feel")+
	coord_flip(ylim=c(1,5))+
  theme(legend.position="none")+
  scale_color_manual(values=colors)+
  theme(axis.text.y=element_text(size=8))

g2=ggplot(t_format %>% filter(attribute %in% c("MF")))
g2=g2+geom_histogram(aes(x=value),
                 bins=5,
                 color='black')+
	theme_classic(base_size=18)+
  scale_y_continuous("")+
  scale_x_continuous("")
cowplot::plot_grid(g1,g2,rel_widths=c(.8,.5), rel_heights=c(1,.5),nrow=1,ncol=2)

```


## Perceived ABV
```{r}

g1=ggplot(t_format %>% filter(attribute %in% c("ABV")))
g1=g1+stat_summary(aes(x=reorder(beer_name, value), 
                   y = value, 
                   color=(beer %in% c(1,5))), 
               fun.data = mean_se)+
	theme_classic(base_size=18)+
	scale_x_discrete("")+
	scale_y_continuous("Perceived ABV")+
	coord_flip()+
  theme(legend.position="none")+
  scale_color_manual(values=colors)+
  theme(axis.text.y=element_text(size=8))

g2=ggplot(t_format %>% filter(attribute %in% c("ABV")))
g2=g2+geom_histogram(aes(x=value),
                 color='black')+
	theme_classic(base_size=18)+
  scale_y_continuous("")+
  scale_x_continuous("")
cowplot::plot_grid(g1,g2,rel_widths=c(.8,.5), rel_heights=c(1,.5),nrow=1,ncol=2)

```




## Taste, Aroma, Mouth Feel Correlations

```{r}
sum_t = t_format %>% 
      group_by(attribute, beer, beer_name, TRUE_ABV) %>%
      summarize(mu=mean(value), sd = sd(value)/sqrt(n())) %>%
      gather(key=estimator, value=value, -attribute, -beer, -beer_name, -TRUE_ABV) %>%
      mutate(attribute_est=paste(attribute,estimator,sep="_")) %>%
      ungroup() %>%
      select(attribute_est,value,beer, beer_name, TRUE_ABV) %>%
      spread(key=attribute_est,value=value)

simple_t = t_format %>% 
  select(attribute, value, Email.Address, beer_name, TRUE_ABV, Sex) %>%
  spread(key=attribute, value=value)

#all_t_spread = t_format %>% 
#      filter(attribute %in% c("taste")) %>%
#      mutate(beer_attribute = paste(beer, beer_name, attribute)) %>%
#      select(beer_attribute, value, Email.Address) %>%
#      spread(key=beer_attribute,value=value)

#M=cor(as.matrix(all_t_spread[,2:dim(all_t_spread)[2]]))
#corrplot(M, type="upper", order="hclust", col = brewer.pal(n=9, name="Spectral"), bg="darkgreen")

```



```{r fig.width=9,fig.height=3}

m0=lm(taste~Aroma, data=simple_t)
p_val = summary(m0)$coefficients[2,4]
corr = summary(m0)$r.squared
labels = data.frame(labels=c(paste("P==", signif(p_val,2), sep=""),
                             paste("R==", signif(corr,2), sep="")),
                    x=c(3,3),
                    y=c(1.5,2))

g1=ggplot(sum_t)
g1=g1+geom_point(aes(x=taste_mu,y=Aroma_mu))+
  geom_segment(aes(x=taste_mu-taste_sd,
                   xend=taste_mu+taste_sd,
                   y=Aroma_mu,
                   yend=Aroma_mu))+
  geom_segment(aes(x=taste_mu,
                   xend=taste_mu,
                   y=Aroma_mu-Aroma_sd,
                   yend=Aroma_mu+Aroma_sd))+
  geom_smooth(aes(x=taste_mu,y=Aroma_mu),method='lm',alpha=0,color='darkblue')+
    theme_classic()+
  scale_x_continuous("Taste")+
  scale_y_continuous("Aroma")+
  coord_cartesian(ylim=c(1,5), 
                  xlim=c(1,5))+
  geom_text(aes(x=x,y=y,label=labels), parse=TRUE, data=labels, hjust=0)


m0=lm(taste~MF, data=simple_t)
p_val = summary(m0)$coefficients[2,4]
corr = summary(m0)$r.squared
labels = data.frame(labels=c(paste("P==", signif(p_val,2), sep=""),
                             paste("R==", signif(corr,2), sep="")),
                    x=c(3,3),
                    y=c(1.5,2))


g2=ggplot(sum_t)
g2=g2+geom_point(aes(x=taste_mu,y=MF_mu))+
  geom_segment(aes(x=taste_mu-taste_sd,
                   xend=taste_mu+taste_sd,
                   y=MF_mu,
                   yend=MF_mu))+
  geom_segment(aes(x=taste_mu,
                   xend=taste_mu,
                   y=MF_mu-MF_sd,
                   yend=MF_mu+MF_sd))+
  geom_smooth(aes(x=taste_mu,y=MF_mu),method='lm',alpha=0,color='darkblue')+
    theme_classic()+
  scale_x_continuous("Taste")+
  scale_y_continuous("Mouth Feel")+
  coord_cartesian(ylim=c(1,5), 
                  xlim=c(1,5))+
    geom_text(aes(x=x,y=y,label=labels), parse=TRUE, data=labels, hjust=0)

m0=lm(Aroma~MF, data=simple_t)
p_val = summary(m0)$coefficients[2,4]
corr = summary(m0)$r.squared
labels = data.frame(labels=c(paste("P==", signif(p_val,2), sep=""),
                             paste("R==", signif(corr,2), sep="")),
                    x=c(3,3),
                    y=c(1.5,2))


g3=ggplot(sum_t)
g3=g3+geom_point(aes(x=Aroma_mu,y=MF_mu))+
  geom_segment(aes(x=Aroma_mu-Aroma_sd,
                   xend=Aroma_mu+Aroma_sd,
                   y=MF_mu,
                   yend=MF_mu))+
  geom_segment(aes(x=Aroma_mu,
                   xend=Aroma_mu,
                   y=MF_mu-MF_sd,
                   yend=MF_mu+MF_sd))+
  geom_smooth(aes(x=Aroma_mu,y=MF_mu),method='lm',alpha=0,color='darkblue')+
    theme_classic()+
  scale_x_continuous("Aroma")+
  scale_y_continuous("Mouth Feel")+
  coord_cartesian(ylim=c(1,5), 
                  xlim=c(1,5))+
  geom_text(aes(x=x,y=y,label=labels), parse=TRUE, data=labels, hjust=0)


plot_grid(g1,g2,g3,rel_widths=c(.3,.3,.3), ncol=3, nrow=1)


```



## ABV vs Taste
```{r fig.width=3,fig.height=3}


m0=lm(taste~ABV, data=simple_t)
#m1=lm(taste~TRUE_ABV, data=simple_t)
p_val = summary(m0)$coefficients[2,4]
corr = summary(m0)$r.squared
labels = data.frame(labels=c(paste("P==", signif(p_val,2), sep=""),
                             paste("R==", signif(corr,2), sep="")),
                    x=c(3,3),
                    y=c(4.5,5))

g=ggplot(sum_t)
g=g+geom_point(aes(y=taste_mu,x=ABV_mu))+
  geom_segment(aes(y=taste_mu-taste_sd,
                   yend=taste_mu+taste_sd,
                   x=ABV_mu,
                   xend=ABV_mu))+
  geom_segment(aes(y=taste_mu,
                   yend=taste_mu,
                   x=ABV_mu-ABV_sd,
                   xend=ABV_mu+ABV_sd))+
  geom_smooth(aes(y=taste_mu,x=ABV_mu),method='lm',alpha=0,color='darkblue')+
    theme_classic()+
  scale_x_continuous("Perceived ABV")+
  scale_y_continuous("Taste")+
  coord_cartesian(ylim=c(1,5))+
  geom_text(aes(x=x,y=y,label=labels), parse=TRUE, data=labels, hjust=0)
g
```	


## Comparison to other rankings

```{r fig.width=3,fig.height=3}

m0=lm(BAscore~value, data=t_format %>% filter(attribute %in% c("taste")))
#m1=lm(taste~TRUE_ABV, data=simple_t)
p_val = summary(m0)$coefficients[2,4]
corr = summary(m0)$r.squared
labels = data.frame(labels=c(paste("P==", signif(p_val,2), sep=""),
                             paste("R==", signif(corr,2), sep="")),
                    x=c(1,1),
                    y=c(4.5,5))

g=ggplot(t_format %>% filter(attribute %in% c("taste")))
g+stat_summary(aes(x=BAscore, y = value, group=beer), color='black')+
  geom_smooth(aes(x=BAscore, y = value), color='darkblue', alpha=0, method='lm')+
	theme_classic()+
	scale_color_brewer(palette="Set1")+
	scale_x_continuous("Beer Advocate Score")+
  scale_y_continuous("Beer Tasting Score")+
	coord_cartesian(ylim=c(1,5), xlim=c(1,5))+
  geom_text(aes(x=x,y=y,label=labels), parse=TRUE, data=labels, hjust=0)

```

#Clustering

## clustering of beers

```{r fig.width=7, fig.height=5}

##CLUSTER BEERS

t_vect = t_format %>% 
        mutate(indiv_att = paste(Email.Address, attribute)) %>%
        select(indiv_att, value, beer, beer_name) %>%
        mutate(value=log(value+1)) %>%
        spread(key=indiv_att, value=value)

m_vect = as.matrix(t_vect[,3:dim(t_vect)[2]])
row.names(m_vect) = t_vect$beer_name

PCA_beers = prcomp(m_vect, center=TRUE, scale=TRUE)
PC1 = PCA_beers$sdev[1]/sum(PCA_beers$sdev)
PC2 = PCA_beers$sdev[2]/sum(PCA_beers$sdev)

pca_t = as.data.frame(PCA_beers$x)
g=ggplot(pca_t)
g+geom_point(aes(x=PC1,y=PC2))+
  geom_text_repel(aes(x=PC1,y=PC2,label=rownames(pca_t)))+
  theme_classic()+
  scale_x_continuous(paste("PC1 (", signif(PC1*100,4), "%)", sep=""))+
  scale_y_continuous(paste("PC2 (", signif(PC2*100,4), "%)", sep=""))

```


## clustering of people

```{r fig.width=8, fig.height=3}

##CLUSTER PEOPLE

colors=brewer.pal(2, "Set1")

t_vect_ABV = t_format %>% 
        filter(attribute=="ABV") %>%
        mutate(indiv_att = paste(Email.Address, attribute)) %>%
        select(indiv_att, value, beer, beer_name) %>%
        mutate(value=log(value+1)) %>%
        spread(key=indiv_att, value=value)

t_vect_taste = t_format %>% 
        filter(attribute=="taste") %>%
        mutate(indiv_att = paste(Email.Address, attribute)) %>%
        select(indiv_att, value, beer, beer_name) %>%
        mutate(value=log(value+1)) %>%
        spread(key=indiv_att, value=value)

t_curr = t_vect_ABV
m_vect = as.matrix(t_curr[,3:dim(t_curr)[2]])
row.names(m_vect) = t_curr$beer_name

PCA_ppl = prcomp(t(m_vect), center=TRUE, scale=TRUE)
PC1 = PCA_ppl$sdev[1]/sum(PCA_beers$sdev)
PC2 = PCA_ppl$sdev[2]/sum(PCA_beers$sdev)

pca_ppl_t = as.data.frame(PCA_ppl$x)
pca_ppl_t$info = rownames(pca_ppl_t)
pca_ppl_t = pca_ppl_t %>% separate(info, c("ID","host","attribute"),sep="@| ")

g_ABV=ggplot(pca_ppl_t)
g_ABV=g_ABV+geom_point(aes(x=PC1,y=PC2,color=attribute))+
  geom_text_repel(aes(x=PC1,y=PC2,label=ID))+
  theme_classic()+
  scale_x_continuous(paste("PC1 (", signif(PC1*100,4), "%)", sep=""))+
  scale_y_continuous(paste("PC2 (", signif(PC2*100,4), "%)", sep=""))+
  scale_color_manual("", values=colors[1], labels="Perceived\nABV")+
  theme(legend.position = "bottom")

t_curr = t_vect_taste
m_vect = as.matrix(t_curr[,3:dim(t_curr)[2]])
row.names(m_vect) = t_curr$beer_name

PCA_ppl = prcomp(t(m_vect), center=TRUE, scale=TRUE)
PC1 = PCA_ppl$sdev[1]/sum(PCA_beers$sdev)
PC2 = PCA_ppl$sdev[2]/sum(PCA_beers$sdev)

pca_ppl_t = as.data.frame(PCA_ppl$x)
pca_ppl_t$info = rownames(pca_ppl_t)
pca_ppl_t = pca_ppl_t %>% separate(info, c("ID","host","attribute"),sep="@| ")

g_taste=ggplot(pca_ppl_t)
g_taste=g_taste+geom_point(aes(x=PC1,y=PC2,color=attribute))+
  geom_text_repel(aes(x=PC1,y=PC2,label=ID))+
  theme_classic()+
  scale_x_continuous(paste("PC1 (", signif(PC1*100,4), "%)", sep=""))+
  scale_y_continuous(paste("PC2 (", signif(PC2*100,4), "%)", sep=""))+
  scale_color_manual("", values=colors[2], labels="Taste")+
  theme(legend.position = "bottom")


plot_grid(g_taste,g_ABV, ncol=2)


```



# Mayflower Porter #1 vs Mayflower Porter #9
## Overall Consistency 

```{r fig.width=8, fig.height=3}

data = t_format %>% 
  filter(beer %in% c(1,9)) %>%
  separate(Email.Address, c("ID","address"), sep="@") %>%
  select(ID, Sex, attribute, value, beer) %>%
  mutate(beer = paste("beer",beer, sep="")) %>%
  select(beer, ID, Sex, value, attribute) %>%
  spread(key=beer, value=value) %>%
  mutate(delta=beer1-beer9)


g2=ggplot(data)
g2=g2+geom_histogram(aes(x=delta, fill=attribute),bins=12)+
  geom_vline(xintercept = 0,linetype=2)+
	theme_classic(base_size=18)+
  facet_wrap(~attribute, nrow=1)+
  scale_x_continuous("change from first taste to second taste")+
  theme(legend.position="none")+
  scale_fill_brewer(palette="Set1")

g2


```

## Individual Ranking Consistency
```{r fig.width=8, fig.height=3}

g1=ggplot(data)
g1=g1+geom_segment(aes(x=0, xend=delta, y=ID, yend=ID, color=attribute))+
  geom_point(aes(x=delta, y=ID, color=attribute))+
	theme_classic(base_size=18)+
  facet_wrap(~attribute, nrow=1)+
  theme(legend.position="none")+
  scale_color_brewer(palette="Set1")+
  scale_x_continuous("change from first taste to second taste",lim=c(-3,3))+
  scale_y_discrete("")

g1

```




# Percieved vs True ABV
```{r fig.width=8,fig.height=3}

m0=lm(ABV~TRUE_ABV, data=simple_t)
p_val = summary(m0)$coefficients[2,4]
corr = summary(m0)$r.squared
labels = data.frame(labels=c(paste("P==", signif(p_val,2), sep=""),
                             paste("R==", signif(corr,2), sep="")),
                    x=c(3,3),
                    y=c(1,2))

g1=ggplot(sum_t)
g1=g1+geom_point(aes(x=TRUE_ABV,y=ABV_mu))+
  geom_segment(aes(x=TRUE_ABV,
                   xend=TRUE_ABV,
                   y=ABV_mu-ABV_sd,
                   yend=ABV_mu+ABV_sd))+
  geom_smooth(aes(x=TRUE_ABV,y=ABV_mu),method='lm',alpha=0,color='darkblue')+
    theme_classic()+
  scale_x_continuous("actual ABV")+
  scale_y_continuous("perceived ABV")+
  coord_cartesian(ylim=c(0,13), xlim=c(0,13))+
  geom_text(aes(x=x,y=y,label=labels), parse=TRUE, data=labels, hjust=0)+
  geom_abline(slope=1,intercept=0)

g2=ggplot(t_format %>% filter(attribute %in% c("ABV")))
g2=g2+stat_summary(aes(x=ABV, y = value, color=Sex, group=interaction(beer,Sex)), size=.2)+
  geom_smooth(aes(x=ABV,y=value, color=Sex),method='lm',alpha=0)+
	theme_classic()+
	scale_color_brewer("",palette="Set1")+
  scale_x_continuous("actual ABV")+
  scale_y_continuous("perceived ABV")+
	coord_cartesian(ylim=c(0,13), xlim=c(0,13))+
  theme(legend.position=c(.2,.8))+
  geom_abline(slope=1,intercept=0)


g3=ggplot(t_format %>% filter(attribute %in% c("ABV")))
g3=g3+geom_violin(aes(y=value,x=Sex, fill=Sex))+
  stat_summary(aes(y=value,x=Sex),geom="crossbar",fun.data=mean_se)+
	theme_classic()+
	scale_fill_brewer("",palette="Set1")+
  scale_y_continuous("perceived ABV")+
  theme(legend.position="None")

plot_grid(g1,g2, g3, ncol=3, rel_widths = c(.4,.4,.2))



sex_test_t = t_format %>% 
            filter(attribute %in% c("ABV")) %>%
            mutate(delta=value-ABV)

t.test(value~Sex,sex_test_t)
wilcox.test(value~Sex,sex_test_t)
#t.test(delta~Sex,sex_test_t)
#wilcox.test(delta~Sex,sex_test_t)

```

```{r fig.width=5,fig.height=3}

g1=ggplot(t_format %>% filter(attribute %in% c("ABV")) %>% filter(Lab %in% c("Burge", "Li")))
g1=g1+stat_summary(aes(x=ABV, y = value, color=Lab, group=interaction(beer,Lab)), size=.2)+
  geom_smooth(aes(x=ABV,y=value, color=Lab),method='lm',alpha=0)+
	theme_classic()+
	scale_color_brewer("",palette="Set1")+
  scale_x_continuous("actual ABV")+
  scale_y_continuous("perceived ABV")+
	coord_cartesian(ylim=c(0,13), xlim=c(0,13))+
  theme(legend.position=c(.2,.8))+
  geom_abline(slope=1,intercept=0)
g1

g2=ggplot(t_format %>% filter(attribute %in% c("ABV")) %>% filter(Lab %in% c("Burge", "Li")))
g2=g2+geom_violin(aes(y=value,x=Lab, fill=Lab))+
  stat_summary(aes(y=value,x=Lab),geom="crossbar",fun.data=mean_se)+
	theme_classic()+
	scale_fill_brewer("",palette="Set1")+
  scale_y_continuous("perceived ABV")+
  theme(legend.position="None")


# t_pie = t_format %>% 
#   filter(Lab %in% c("Burge", "Li")) %>%
#   select(Email.Address, Sex, Lab) %>%
#   unique() %>%
#   group_by(Sex,Lab)
# 
# g3=ggplot(t_pie)
# g3=g3+geom_bar(aes(x=Lab, fill=Sex), position="dodge",width=.3)+
#   theme_classic()+
#   scale_fill_brewer(palette="Set1")+
#   theme(legend.position = "none")
# 
# plot_grid(g1,g2,g3, ncol=3, rel_widths = c(.6,.2,.2))



```


# Male vs Female preferences


```{r fig.width=10, fig.height=4}

t_sum = t_format %>% 
		group_by(Sex,attribute, beer_name) %>%
		summarize(mu = mean(value)) %>%
		group_by(beer_name, attribute) %>%
		mutate(min_val=min(mu))

t_sum_line = t_sum %>% 
				spread(key=Sex, value=mu) %>%
				mutate(sex_col=ifelse(Female>Male,"Female","Male"))

g1=ggplot(t_sum %>% filter(attribute %in% c("taste")))
g1=g1+geom_segment(aes(y=Male, 
				 yend=Female, 
				 x=reorder(beer_name, min_val), 
				 xend=reorder(beer_name, min_val),
				 color=sex_col), 
			   data=t_sum_line %>% filter(attribute %in% c("taste")), 
			   size=1.2)+
	stat_summary(aes(x=reorder(beer_name, 
							   min_val), 
				 y = mu, 
				 color=Sex), 
				 fun.y=mean, 
				 geom="point",
				 size=2)+
	theme_classic()+
	scale_color_brewer("",palette="Set1")+
	coord_cartesian(ylim=c(1,5))+
	scale_x_discrete("")+
  scale_y_continuous("Taste")+
	coord_flip()+
  theme(legend.position="bottom")


g2=ggplot(t_sum %>% filter(attribute %in% c("Aroma")))
g2=g2+geom_segment(aes(y=Male, 
				 yend=Female, 
				 x=reorder(beer_name, min_val), 
				 xend=reorder(beer_name, min_val),
				 color=sex_col), 
			   data=t_sum_line %>% filter(attribute %in% c("Aroma")), 
			   size=1.2)+
	stat_summary(aes(x=reorder(beer_name, 
							   min_val), 
				 y = mu, 
				 color=Sex), 
				 fun.y=mean, 
				 geom="point",
				 size=2)+
	theme_classic()+
	scale_color_brewer("",palette="Set1")+
	coord_cartesian(ylim=c(1,5))+
	scale_x_discrete("")+
  scale_y_continuous("Aroma")+
	coord_flip()+
  theme(legend.position="bottom")


g3=ggplot(t_sum %>% filter(attribute %in% c("MF")))
g3=g3+geom_segment(aes(y=Male, 
				 yend=Female, 
				 x=reorder(beer_name, min_val), 
				 xend=reorder(beer_name, min_val),
				 color=sex_col), 
			   data=t_sum_line %>% filter(attribute %in% c("MF")), 
			   size=1.2)+
	stat_summary(aes(x=reorder(beer_name, 
							   min_val), 
				 y = mu, 
				 color=Sex), 
				 fun.y=mean, 
				 geom="point",
				 size=2)+
	theme_classic()+
	scale_color_brewer("",palette="Set1")+
	coord_cartesian(ylim=c(1,5))+
	scale_x_discrete("")+
  scale_y_continuous("Mouth Feel")+
	coord_flip()+
  theme(legend.position="bottom")


plot_grid(g1,g2,g3,ncol=3)



```


#Inter-Lab Beer Preferences
## Burge vs Li Lab Preferences
```{r fig.width=8, fig.height=4}

lab_sum = t_format %>% filter(Lab %in% c("Burge", "Li")) %>%
	group_by(Lab, attribute, beer_name, beer) %>%
	summarize(mu = mean(value), sd = sd(value)) %>%
	mutate(lab_attribute = interaction(Lab, attribute)) %>%
	ungroup() %>%
	select(lab_attribute, mu, beer_name, beer)

spread_data = lab_sum %>% spread(key=lab_attribute, value=mu)

##Beers Li lab liked, we didn't
g1=ggplot(spread_data)
g1=g1+geom_point(aes(x=Burge.taste, y=Li.taste))+
	geom_text_repel(aes(x=Burge.taste, y=Li.taste, label=beer))+
	theme_classic()+
	coord_cartesian(ylim=c(1,5), xlim=c(1,5))+
	geom_abline(slope=1,intersect=0)

g2=ggplot(spread_data)
g2=g2+geom_point(aes(x=Burge.taste, y=Li.taste))+
	geom_text_repel(aes(x=Burge.taste, y=Li.taste, label=beer_name))+
	theme_classic()+
	coord_cartesian(ylim=c(1,5), xlim=c(1,5))+
	geom_abline(slope=1,intersect=0)

plot_grid(g1,g2,ncol=2)


```




## Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
